Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-01-27 colt-21/cvx-flats.tex
Forgot to save a line

\begin{table}
	\begin{center}
	\begin{tabular}{|l||l|l|} 
		\hline
		& \emph{Target loss}  & \emph{Target statistic}\\ \hline \hline
		\emph{Discrete prediction} & \textbf{Q1:} High-confidence classification \S~\ref{sec:finite-calib}  & \textbf{Q2:} Hierarchical prediction App.~\ref{app:omitted-examples}\\ \hline 
		\emph{Continuous estimation} & \textbf{Q3:} AUC Optimization \jessie{??} & \textbf{Q4:} Variance, entropy, and norms \S~\ref{sec:contin-consis} \\ 
		& \cite{gao2012consistency} & \\
		\hline
	\end{tabular}
\caption{The four quadrants of problem types, with an example of interest for each.}
\label{tab:quadrants}
\end{center}
\end{table}

>>>>

\begin{table}
	\begin{center}
	\begin{tabular}{|l||l|l|} 
		\hline
		& \emph{Target loss}  & \emph{Target statistic}\\ \hline \hline
		\emph{Discrete prediction} & \textbf{Q1:} High-confidence classification \S~\ref{sec:finite-calib}  & \textbf{Q2:} Hierarchical prediction App.~\ref{app:omitted-examples}\\ \hline 
		\emph{Continuous estimation} & \textbf{Q3:} AUC Optimization \jessie{??} & \textbf{Q4:} Variance, entropy, and norms \S~\ref{sec:contin-consis} \\ 
		& \citet{gao2012consistency} & \\
		\hline
	\end{tabular}
\caption{The four quadrants of problem types, with an example of interest for each.}
\label{tab:quadrants}
\end{center}
\end{table}
